Arrangement for DroneGo

### 2020-03-09 PAPER.tex
Updates from Overleaf

% 本模板不需要填写年份，以当前电脑时间自动生成
% 请在以下的方括号中填写队伍控制号
\usepackage[1234567]{easymcm}  % 载入 EasyMCM 模板文件
\problem{F}  % 请在此处填写题号
\usepackage{mathptmx}  % 这是 Times 字体，中规中矩 
%\usepackage{mathpazo}  % 这是 COMAP 官方杂志采用的更好看的 Palatino 字体，可替代以上的 mathptmx 宏包

\usepackage{rotating}
\usepackage{colortbl}
\usepackage{booktabs}

@@

% 此处填写摘要内容
\begin{abstract}
    After the worst hurricane to ever hit Puerto Rico, lots of people were
    injured. Highways and roads were blocked and damaged by the flood. We
    establish a model to both meet the needs of medicine delivery and road
    reconnaissance with rotor wing drones.

    Our model takes into account the following factors: the number of cargo
    containers, the type and the number of drones, the number of medicines,
    the associated packing configuration for each cargo container, the exact locations of cargo containers, and the schedule for each drone. Before establishing the model, we develop necessary assumptions and essential notations to make a reliable scenario.

    After analyzing the locations of hospitals and flight distance of drones,
    we decide to set three containers because of the long distance among hospitals. Then, we quantify the associated packing configuration quality by
    the following three aspects: the minimum time to complete medical supply delivery, the amount of medical supply, and the reconnaissance ability.

    We use AHP Algorithm and the normalization method to determine the
    weights of these three factors and evaluate the Comprehensive Evaluation
    (CE) value. Then we use the greedy algorithm to get the best-associated
    packing configuration with the highest CE value under the ideal condition.

    After that, we choose the approximate optimal positions for all cargo
    containers by image analysis to determine the optimate associated packing
    configuration in reality (using Bisection). We process the map of roads and
    populated places into pixels. Then, we can determine the exact location of
    containers by counting the occupied pixels of roads and populated places.

    We provide the schedule plan for each drone. Then, we test our model
    and provide the evidence to show the stability and reliability of the work. In
    the end, we analyze the strengths and weakness of the model and conclude
    the result in our report.

@@

\subsection{Our work}
%A literatrue\cite{1} say something about this problem ...
To help the UN address the increasing challenge of EDPs, We need to develop a set of models for resettling policies that take into account the protection of human rights and the protection of culture. And we have done the following work: 
1. By predicting the future sea-level rise, estimate the potential EDPs and regions.
2. to analyze the risk of loss of the culture behind the EDPs. 
3. to guarantee the human rights of the EDPs, we established the evaluation models to arrange EDPs’ migration properly and provides  reference objectively 
4. According to the established model, our team designed the policies from two aspects: protecting human rights and protecting local culture.

%\begin{enumerate}[\bfseries 1.]
%    \item We do ...
%    \item We do ...
%    \item We do ...
%\end{enumerate}
\newpage
\section{Assumptions}

@@

\newpage
\section{Notations}
The primary notations used in this paper are listed in Table \ref{tb:notation}.
\begin{table}[!htbp]
\begin{center}
\caption{Notations}
\begin{tabular}{cl}
	\toprule
	\multicolumn{1}{m{3cm}}{\centering Symbol}
	&\multicolumn{1}{m{8cm}}{\centering Definition}\\
	\midrule
	$A$&the first one\\
	$b$&the second one\\
	$\alpha$ &the last one\\
	$A$&the first one\\
	$b$&the second one\\
	$\alpha$ &the last one\\
	$A$&the first one\\
	$b$&the second one\\
	$\alpha$ &the last one\\
	$A$&the first one\\
	$b$&the second one\\
	$\alpha$ &the last one\\
	$A$&the first one\\
	$b$&the second one\\
	$\alpha$ &the last one\\
	\bottomrule
\end{tabular}\label{tb:notation}
\end{center}
\end{table}
\newpage

@@

\item Standardize the data obtained

\item Factor model

%行内公式加$符号

@@

\begin{equation}
    Y_i=F_i\times k_i
\end{equation}

@@

% Table generated by Excel2LaTeX from sheet 'Sheet2'
\begin{table}[htbp]
  \centering
  \caption{Sea level forecast for a particular year}
    \begin{tabular}{c|ccc}
    \toprule
    \multicolumn{1}{l|}{\kappa} & 2030  & 2050  & 2100 \\
    \midrule
    0.6   & 5.5   & 11.1  & 30.1 \\
    1.2   & 7.8   & 15.6  & 42.4 \\
    2     & 10.8  & 21.6  & 58.6 \\
    3     & 14.5  & 29    & 78.9 \\
    \bottomrule
    \end{tabular}%
  \label{Sea level forecast for a particular year}%
\end{table}%

@@

\begin{figure}[htbp]\label{5.2}
	\centering
	\includegraphics[width=1\textwidth]{5.2.png}
	\caption{ flow diagram of solution}\label{5.2}
\end{figure}

%6
\section{Preservation of Culture Policy}

@@

%6.2
\subsection{Concrete Policies}
Our team has divided cultural protection into three levels , as shown in figure \ref{culture 3 levels},and proposed corresponding policies.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{culture 3 levels.png}
	\caption{ flow diagram of solution}\label{culture 3 levels}
\end{figure}

@@

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{Countries with eligible immigration indices.png}
	\caption{ flow diagram of solution}\label{Countries_with_eligible_immigration_indices}
\end{figure}

@@

After that, we normalize per capita CO2 emissionss and per capita energy consumption of countries with LCI value greater than 0, and measure their contribution to the National Responsibility Index with a weighting of 50\% each. The corresponding NRI of 57 countries was obtained. The results are shown in figure \ref{NRI}.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{NRI.png}
	\caption{ flow diagram of solution}\label{NRI}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{country_index.png}
	\caption{ flow diagram of solution}\label{country_index}
\end{figure}

We regard countries with an IRI greater than 0.3 to be high. To simplify the subsequent calculations, we used only high-index countries. The result is shown in figure \ref{high_index_countries}.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{high_index_countries.png}
	\caption{ flow diagram of solution}\label{high_index_countries}
\end{figure}

@@

%7.5
\subsection{Comprehensive Index}

%8
\section{Policies for Protection of Human Rights}

>>>>

% 本模板不需要填写年份，以当前电脑时间自动生成
% 请在以下的方括号中填写队伍控制号
\usepackage[2009965]{easymcm}  % 载入 EasyMCM 模板文件
\problem{F}  % 请在此处填写题号
\usepackage{mathptmx}  % 这是 Times 字体，中规中矩 
%\usepackage{mathpazo}  % 这是 COMAP 官方杂志采用的更好看的 Palatino 字体，可替代以上的 mathptmx 宏包

\usepackage{rotating}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{multicol}

@@

% 此处填写摘要内容
\begin{abstract}

As global climate change continues, many island nations are threatened by rising sea levels. As a result, islanders face forced emigration. How to properly relocate these EDPs while ensuring the protection and preservation of their human rights and culture？This is what our team is trying to solve. To design the EDPs policy clearly, we divide the policy into the preservation policy of culture and the protection policy of human rights.

Our first model is the prediction model of potential EDPs. By using the sea level prediction model, we predicted the height of sea-level rise in 2100 (relative to 2000), and we selected 37 island countries at risk around the world based on the sea level rise in 2100 and the characteristics of the islands. We regard their citizens are all potential EDPs, and we estimated the number of potential EDPs. Next, we investigated the number of existing world heritage sites in these island countries and designed a series of preservation policies backed on the actual situation.

Our second model, from a human rights perspective, provides objective support for the design of EDPs' resettlement policies. Firstly, a Liveable Country Index (LCI) was created through the application of factor analysis to measure whether the host country can guarantee the human rights of EDPs. Similarly, the creation of a National Responsibility Index (NRI) to measure each country's responsibility for sea-level rise, namely each country's responsibility for the EDPs. Finally, considering the cost of migration distance, we created a Comprehensive Index from the perspective of risk island countries in different geographical locations, which represents the compatibility between island countries and host countries. We can see that the Comprehensive Index is the result of two-way selection.

According to the Composite Index, we have developed the best resettlement program under the premise of protecting human rights, for the EDPs. On this basis, some migration policies are put forward.At the end of the paper, we analyze the advantages and disadvantages of our model.

@@

\subsection{Our work}
%A literatrue\cite{1} say something about this problem ...
To help the UN address the increasing challenge of EDPs, We need to develop a set of models for resettling policies that take into account the protection of human rights and the protection of culture. And we have done the following work:

1. By predicting the future sea-level rise, estimate the potential EDPs and regions.

2. to analyze the risk of loss of the culture behind the EDPs.

3. to guarantee the human rights of the EDPs, we established the evaluation models to arrange EDPs’ migration properly and provides  reference objectively

4. According to the established model, our team designed the policies from two aspects: protecting human rights and protecting local culture.

%\begin{enumerate}[\bfseries 1.]
%    \item We do ...
%    \item We do ...
%    \item We do ...
%\end{enumerate}
\section{Assumptions}

@@

\newpage
%----------------------------notations---------------------------

\section{Notations}
The primary notations used in this paper are listed in Table \ref{Notations}.
% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
  \centering
  \caption{Notations}
    \begin{tabular}{ll}
    \toprule
    \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{Definition} \\
    \midrule
    $C(t)$  & Global emissions of greenhouse gases in year t \\

    $c_0$    & The initial CO^2 concentration(in 1850) \\
    $F(t)$  & radiative forcing in year t \\
    $a_0,b$  & \textcolor[rgb]{ .133,  .133,  .133}{Constant coefficient} \\
    $T(t)$  & \textcolor[rgb]{ .2,  .2,  .2}{Temperature in year t} \\
    $\beta$  & Specific heat capacity \\
    $\gamma$ & heat capacity ratio  \\
    $\kappa$ & \multicolumn{1}{p{25.555em}}{thermal diffusion coefficient of ocean} \\
    $LCI$   & Liveable Country Index \\
    $NRI$   & \textcolor[rgb]{ .133,  .133,  .133}{National Responsibility Index} \\
    $IRI$   & International Responsibility Index \\
    \toprule
    \end{tabular}%
  \label{Notations}%
\end{table}%

@@

@@

\begin{equation}
    Y_i=F_i\times k_i\,(i=1,2,…n)
\end{equation}

@@

% Table generated by Excel2LaTeX from sheet 'Sheet2'
\begin{table}[htbp]
  \centering
  \caption{Sea level forecast for a particular year}
    \begin{tabular}{cccc}
    \toprule
    \multicolumn{1}{l}{\kappa} & 2030  & 2050  & 2100 \\
    \midrule
    0.6   & 5.5(cm)   & 11.1(cm)  & 30.1(cm) \\
    1.2   & 7.8   & 15.6  & 42.4 \\
    2     & 10.8  & 21.6  & 58.6 \\
    3     & 14.5  & 29    & 78.9 \\
    \bottomrule
    \end{tabular}%
  \label{Sea level forecast for a particular year}%
\end{table}%

@@

\begin{figure}[htbp]\label{5.2}
	\centering
	\includegraphics[width=1\textwidth]{5.2.png}
	\caption{ The geographical locations of 37 island states}\label{5.2}
\end{figure}

\newpage
%6
\section{Preservation of Culture Policy}

@@

%6.2
\subsection{Concrete Policies}
Our team has divided cultural protection into three levels , as shown in figure \ref{culture 3 levels}, and proposed corresponding policies.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{culture 3 levels.png}
	\caption{ Preservation Policy of Culture}\label{culture 3 levels}
\end{figure}

@@

\newpage

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{LCI.png}
	\caption{ Countries with eligible immigration indices }\label{Countries_with_eligible_immigration_indices}
\end{figure}

@@

After that, we normalize per capita $CO^2$ emissionss and per capita energy consumption of countries with LCI value greater than 0, and measure their contribution to the National Responsibility Index with a weighting of 50\% each. The corresponding NRI of 57 countries was obtained. The results are shown in figure \ref{NRI}.

\newpage
\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{NRI.png}
	\caption{ International Responsibility Index}\label{NRI}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{IRI.png}
	\caption{ Country Index}\label{country_index}
\end{figure}

\newpage

%-----------------------------------high index countries-----------------------
We regard countries with an IRI greater than 0.3 to be high. To simplify the subsequent calculations, we used only high-index countries. The result is shown in figure \ref{high_index_countries}.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{high_index_countries.png}
	\caption{High-index Countries}\label{high_index_countries}
\end{figure}

@@

The island nations at risk are scattered across the world's oceans. The influence of geography on resettlement must be taken into account when considering the problem of EDPs. Therefore, we regard the distance between island countries and countries with high IRI as one of the factors determining our policy.

Based on geographical location, we divided the 37 threatened countries into six regions: Caribbean Sea(A), Western Pacific(B), Mediterranean Sea(C), Maritime Southeast Asia(D), Indian Ocean(E), East Atlantic(F). The countries included in each region are shown in figure \ref{6_regions}.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{6_regions.png}
	\caption{ 6 regions}\label{6_regions}
\end{figure}

Bing Map was used to measure the distance between countries with high country index and threatened areas, and the distance was divided into 6 grades, as shown in Table \ref{distance_level}.

% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
  \centering
  \caption{Add caption}
    \begin{tabular}{lllllll}
    \toprule
    Rank  & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{6} \\
    \midrule
    Distance(km) & <3000 & 3000-6000 & 6001-9000 & 9001-12000 & 12001-15000 & 15001-18000 \\
    \bottomrule
    \end{tabular}%
  \label{distance_level}%
\end{table}%

After the measurement, we got table \ref{distance}.

% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
  \centering
  \caption{Add caption}
    \begin{tabular}{lcccccc}
    \toprule
    Country & A     & B     & C     & D     & E     & F \\
    \midrule
    Australia & 6     & 2     & 5     & 1     & 4     & 6 \\
    Qatar & 4     & 5     & 2     & 3     & 2     & 3 \\
    Canada & 2     & 4     & 3     & 5     & 5     & 5 \\
    Guyana & 1     & 5     & 3     & 6     & 4     & 3 \\
    Luxembourg & 3     & 6     & 1     & 5     & 3     & 2 \\
    Norway & 3     & 5     & 2     & 4     & 3     & 3 \\
    United States & 1     & 4     & 3     & 6     & 5     & 3 \\
    Kazakhstan & 4     & 4     & 2     & 3     & 3     & 3 \\
    Finland & 3     & 5     & 2     & 4     & 3     & 3 \\
    \bottomrule
    \end{tabular}%
  \label{distance}%
\end{table}%

%7.5
\subsection{Comprehensive Index}
For more careful consideration, IRI and distance grade was used as the comprehensive indexes to select suitable countries for EDPs to resettle. Closer proximity means lower resettlement costs and, to some extent, it protect EDPs' way of life. The evaluation system of the comprehensive index was defined as:

\begin{equation}
    Comprehensive\,\,Index=IRI-\frac{Distance\,\,grade}{Maximum\,\,Distance\,\,grade}+0.6
\end{equation}

The 0.6 here is to prevent the composite index from being negative, which would affect the comparison between the results.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{ABCDEF.png}
	\caption{ flow diagram of solution}\label{ABCDEF}
\end{figure}

\newpage

%-------------------------------------8
\section{Policies for Protection of Human Rights}

%-------------------------------------9
\section{Strengths and Weaknesses}
